---
title: "HW5"
output: html_document
date: "2022-11-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)
library(janitor)
library(ggplot2)

```

#1
```{r}
poke_data1 <- read.csv("Pokemon.csv")

poke_data<-clean_names(poke_data)


```

The clean names function took the column names and turned them lowercase as well as turned periods into underscores.

#2
```{r}
pokebar <- ggplot(poke_data, aes(y=type_1)) + geom_bar()

pokebar

poke_data_f <-subset(poke_data,type_1 %in% c("Bug","Fire","Grass","Normal","Water","Psychic"))  

poke_data_f$type_1 <- as.factor(poke_data_f$type_1)  

poke_data_f$legendary <-as.factor(poke_data_f$legendary)
```
There are 18 types of Pokemon, the types are fairly evenly distributed, with the exception of flying type which has very few, fairy type does have a little less as well. 

#3
```{r}
poke_data_split <- initial_split(poke_data_f, prop=.7, strata = type_1) 

poke_train <- training(poke_data_split)
poke_test <- testing(poke_data_split)

#318 training observations
count(poke_train)
# 140 testing observations
count(poke_test)

poke_folds <- vfold_cv(poke_train, v = 5, stata = type_1)

```
There are multiple categorical outcomes so it is important to stratify again to get accurate cross validation.

#4
```{r}
poke_re <- recipe(type_1 ~ legendary + generation+sp_atk+attack+speed+defense+hp+sp_def, data = poke_train) %>% step_dummy(c(legendary,generation)) %>% step_normalize(all_numeric_predictors())


```
